Pre-processing Data from Embedded Questions NoContext Corpus Study

### 2022-11-14 analysis/03_experiment/rscripts/pre-processing.Rmd
raw bar plots with correct para order

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/overall_raw.pdf",width=3.5,height=3)
```

>>>>

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/1a_overall_raw.pdf",width=3.5,height=3)
```

### 2022-11-14 analysis/04_experiment/rscripts/pre-processing.Rmd
raw bar plots with correct para order

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/overall_raw.pdf",width=3.5,height=3)
```

>>>>

# Re-Order the paraphrase levels so 'the' is green
agr$paraphrase <- factor(agr$paraphrase, levels=c("a","every","the","other"))

ggplot(agr,aes(x=paraphrase, y=mean_rating, fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  # ggtitle("Overall mean rating for each paraphrase") +
  xlab("Paraphrase") +
  ylab("Mean rating") +
  theme(legend.position = "none") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1b_overall_raw.pdf",width=3.5,height=3)
```

### 2022-11-14 analysis/06_experiment/rscripts/pre-processing.Rmd
raw bar plots with correct para order

>>>>

# Violin plot
```{r}
agr = test %>%
  group_by(tgrep_id, paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>% #
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

# Re-Order the paraphrase levels so 'the' is green
agr$paraphrase <- factor(agr$paraphrase, levels=c("a","every","the","other"))

grand_mean = test %>%
  group_by(paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) +
    geom_violin(trim=FALSE,alpha=.4) +
    geom_point(grand_mean, size=3, color="black") +
    geom_errorbar(grand_mean,aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
    ylim(0,1) +
    scale_fill_manual(values=cbPalette) +
    scale_color_manual(values=cbPalette)

# ggsave("../graphs/1a_violin-raw.pdf",width=4,height=2)
